Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2

### 2023-02-01 Paper/paper.tex
updated paper

Autonomous driving software architectures follow the "\textit{Sense - Think - Act}" paradigm \cite{murphy2000}, as shown in Figure \ref{fig:autonomous_driving_architecture}. Most architectures implement a hierarchical structure in which sensory inputs are processed to create an environmental representation, leading to a path from the current position to the destination computed by global planning. This is followed by behavioral planning, which ensures that the vehicle obeys traffic rules, and local planning, which translates motion commands while taking into account system constraints. An additional system monitoring layer monitors the execution of other components and triggers actions in case of failures \cite{zimmermann2020adaptive}. Vehicles can achieve (Society of Automotive Engineers) SAE levels of autonomy up to levels four and five \cite{bacha2008odin}. Expanding the behavior planning module can lead to higher levels of autonomy \cite{reke2020}.

@@

In this work, the Robot Operating System 2.0 (ROS2) \cite{ros2022} framework was selected as the platform to test the hypothesis. ROS2 is a newer version of the open-source middleware, Robot Operating System (ROS) \cite{quigley2009}, that has received updates to its architecture and design for improved real-time safety, certification, and security for industrial applications. ROS2's Nav2 package, which is used for navigation and localization, has some limitations. For example, it may not handle events such as slipping wheels or orientation changes by external influences appropriately. This can lead to erratic movement of the robot, as well as incorrect planning commands. In severe cases, the robot may continue to drive despite incorrect interpretation of its surroundings, which is highly unsafe and requires manual intervention. Therefore, to achieve higher levels of autonomy, it is necessary to define requirements that address these limitations and elevate the level of safety and reliability.

@@

The limitations of the standard ROS and Navigation2 setup for mobile robots were identified and used to derive software requirements for improving the robot's behavior. The non-functional requirements and their descriptions are listed in Table \ref{tab:fn_req}. The functional requirements and their acceptance criteria are also listed in the same table, with prioritization based on the severity of consequences for the system. The first six functional requirements prioritize safety and robustness, while functional requirements seven to nine focus on increasing robot autonomy with lower risk potential.

@@

This work focuses on extending the capabilities of a mobile robot system by adding an autonomous layer to the existing navigation setup. The requirements for improving the robot's behavior were derived from the limitations of the current setup and are prioritized based on their severity. The autonomy layer is designed to increase the robustness and autonomy of the whole system and includes three main components: a system supervisor, a data storage system, and a behavior planner. The system supervisor monitors the health of all components, including sensors and navigation, and provides constant execution monitoring. The data storage system stores relevant system information and data, allowing for more deliberative behaviors. The behavior planner processes information from the execution checker, the navigation system, and sensor data to make decisions on how to increase autonomy. Finally, a decision gate is needed to intelligently switch between speed commands from the navigation system and the autonomy layer. A block diagram of the proposed system is shown in Figure \ref{fig:block_diagram}.

@@

The system supervisor component uses a Watchdog design pattern to monitor the system and take corrective measures when problems are detected. The component operates partly outside the behavior tree's thread to avoid blocking its execution. The component receives messages from nodes and informs the behavior tree of problems with a node through a provided service. The behavior tree uses service calls to check component health in Condition Nodes. If a node fails, the robot slows down and tries to restart the sensor. If the restart fails twice, the robot stops. The timeout for declaring a node failed is set to one second.

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/top_level_bt.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure*}

@@

The battery behavior monitors the robot's battery and decides if the robot should navigate to a new goal location. The decision is based on the current battery charge and the estimated energy consumption to reach the new goal. The energy expenditure was predicted using a linear function and considering the idle consumption and energy to drive the motors. A safety factor was added to the energy estimation function to consider scenarios where the robot may need to stop navigation.. A battery package was created for simulation purposes and updates the battery charge every second. The battery package subscribes to the command velocity topic and decreases the battery charge for every message received. The consumption rates are not close to reality but were chosen for rapid testing.

@@

The battery module estimates the remaining charge by taking the battery voltage, the power consumption of every component and the movement of the robot into account thus assuring that the robot has enough charge left to navigate to a given goal. Following function is used to determine the current state of charge of the battery: \[Batt_{SoC}(t) = Batt_{SoC}(t-1)-\frac{\frac{P_{components}}{V_{measured}}}{Batt_{capacity}}* t_{timestep} *100\] where $Batt_{SoC}$ is the charge in percentage, $t$ is the time of calculation in hours, $t_{timestep}$ the time step in seconds and $P_{components}$ the combined power consumption of every component connected to the robot in Watt. $P_{components}$ changes depending on the speed of the robot. The calculation assumes a fully charged battery.

@@

The scenarios, derived from functional requirements, test multiple requirements as listed in tables \ref{tab:behavior_scenarios} and \ref{tab:sensor_scenarios}. To be counted as a success, all acceptance criteria for a scenario must be met. The scenarios are conducted by shutting down sensor drivers, publishing navigation goals, and simulating obstacles and battery conditions. Examples include: NoPathFound$_1$ tests recovery from inability to plan, NoPathFound$_2$ tests alternative goal navigation, Collision$_1$ tests maneuvering out of collisions, Collision$_2$ tests recovering from crashes, and Battery$_1$ tests low battery navigation.

\begin{table}[ht]
	\centering
	\caption{Behavior Scenarios}
	\label{tab:behavior_scenarios}
	\renewcommand{\arraystretch}{1.25}
	\resizebox{0.95\linewidth}{!}{%
		\begin{tabular}{| m{0.11\linewidth} | m{0.19\linewidth}| m{0.4\linewidth} | m{0.3\linewidth}|} 
			\hline
			\textbf{Name} & \textbf{Requirements} & \textbf{Description} & \textbf{Success Criteria}\\ 
			\hline	
			NoPath Found$\_$1 & fn$\_$req7 & Path to goal can not be calculated, robot is standing still & 
			Reset system, calculate path to goal, reach goal \\
			\hline
			NoPath Found$\_$2 & fn$\_$req7, fn$\_$req8 & Goal is unreachable, robot is standing still & Alternative goals, close to the original are tested to be reachable \\
			\hline
			Collision$\_$1 & fn$\_$req2, fn$\_$req4, fn$\_$req6 & Robot is standing still and a collision with the robot is caused & Robot can get out of collision state, navigation to goals still working \\
			\hline
			Collision$\_$2 & fn$\_$req2, fn$\_$req4, fn$\_$req6 & The robot is driving and collides with an undetected obstacle (0.25m/s) & 
			Robot can get out of collision state, navigation to goals still working, undetected obstacle gets added to map \\
			\hline
			Battery$\_$1 & fn$\_$req9 & The robot battery runs low & The robot will not drive to a goal that is outside of its reachable range \\
			\hline	
		\end{tabular}
	}
\end{table}

\begin{table}[ht]
	\centering
	\caption{Sensor Scenarios}
	\label{tab:sensor_scenarios}
	\renewcommand{\arraystretch}{1.25}
	\resizebox{0.95\linewidth}{!}{%
		\begin{tabular}{| m{0.1\linewidth}| m{0.1\linewidth} | m{0.2\linewidth}| m{0.3\linewidth} | m{0.3\textwidth}|} 
			\hline
			\textbf{Sensor Tested} & \textbf{Name} & \textbf{Requirements }& \textbf{Description} & \textbf{Success Criteria}\\ 
			\hline
			& Lidar$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, Lidar node crashes & Reset the system\\ 
			\cline{2-5}
			Lidar &Lidar$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			& Lidar$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
			& IMU$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, IMU node crashes & Reset system \\
			\cline{2-5}
			IMU &IMU$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			&IMU$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
			& Odom$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, Odom node crashes & Reset the system\\ 
			\cline{2-5}
			Odometry &Odom$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			&Odom$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
		\end{tabular}
	}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Results}
	\label{tab:results}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.95\linewidth}{!}{%
		\begin{tabular}{| m{0.25\linewidth} | m{0.15\linewidth}| m{0.3\linewidth} | m{0.3\linewidth}|} 
			\hline
			\multirow{2}{*}{\textbf{Name}} & \multirow{2}{0.11\textwidth}{\textbf{Number of Runs}} & \multicolumn{2}{|c|}{\textbf{Percentage Successful}} \\
			\cline{3-4}
			& & \textbf{Without BT} & \textbf{With BT} \\
			\hline
			Lidar$\_$1 & 5 & 0 & 100 \\ 
			\hline
			Lidar$\_$2 & 5 & 0 & 100 \\ 
			\hline
			Lidar$\_$3 & 5 & 0 & 100 \\ 
			\hline
			IMU$\_$1 & 5 & 0 & 100 \\ 
			\hline
			IMU$\_$2 & 5 & 0 & 100 \\ 
			\hline
			IMU$\_$3 & 5 & 0 & 100 \\ 
			\hline
			Odom$\_$1 & 5 & 0 & 100 \\ 
			\hline
			Odom$\_$2 & 5 & 0 & 100 \\ 
			\hline
			Odom$\_$3 & 5 & 0 & 100 \\ 
			\hline
			NoPath Found$\_$1 & 20 & 0 & 100 \\ 
			\hline
			NoPath Found$\_$2 & 20 & 0 & 55 \\ 
			\hline
			Collision$\_$1 & 20 & 0 & 95 \\ 
			\hline
			Collision$\_$2 & 20 & 0 & 100 \\ 
			\hline
			Battery$\_$1 & 10 & 0 & 100 \\ 
			\hline
		\end{tabular}
	}
\end{table}

However, there is a lack of intelligence and autonomy when the robot stands still, and a collision is forced. The test showed potential shortcomings of the implemented collision behavior. The results show that the functional requirements (as defined in \ref{tab:fn_req}) are met in almost all cases, with the exception of fn$_req6$ and fn$_req8$. The architectural design choices meet all the non-functional requirements. The system's performance when checking the conditions of the BT is below the desired threshold of $10ms$, allowing for efficient execution of behavior tree cycles.

The system also performed well in terms of performance, with the whole system running in multiple threads, allowing the behavior tree to complete one complete execution cycle in about 5ms. Overall, the results suggest that the implemented behavior planning and system supervision system is a promising solution for autonomous navigation in complex environments.

>>>>

Autonomous driving software architectures follow the "\textit{Sense - Think - Act}" paradigm \cite{murphy2000}, as shown in Figure \ref{fig:autonomous_driving_architecture}. Most architectures implement a hierarchical structure in which sensory inputs are processed to create an environmental representation, leading to a path from the current position to the destination computed by global planning. This is followed by behavioral planning, which ensures that the vehicle obeys traffic rules, and local planning, which translates motion commands while taking into account system constraints. An additional system monitoring layer monitors the execution of other components and triggers actions in case of failures \cite{zimmermann2020adaptive}. Vehicles can achieve Society of Automotive Engineers (SAE) levels of autonomy up to levels four and five \cite{bacha2008odin}. Expanding the behavior planning module can lead to higher levels of autonomy \cite{reke2020}.

@@

In this work, the Robot Operating System 2.0 (ROS2) \cite{ros2022} framework was selected as the platform to test the hypothesis. ROS2 is a newer version of the open-source middleware, Robot Operating System (ROS) \cite{quigley2009}, that has received updates to its architecture and design for improved real-time safety, certification, and security for industrial applications. ROS2's Nav2 package, which is used for navigation and localization, has some limitations. For example, it may not handle events such as slipping wheels or orientation changes by external influences appropriately. This can lead to erratic movement of the robot, as well as incorrect planning commands. In severe cases, the robot may continue to drive despite incorrect interpretation of its surroundings, which is highly unsafe and requires human intervention. Therefore, to achieve higher levels of autonomy, it is necessary to define requirements that address these limitations and elevate the level of safety and reliability.

@@

The limitations of the standard ROS2 and Navigation2 setup for mobile robots were identified and used to derive software requirements for improving the robot's behavior. The non-functional requirements and their descriptions are listed in Table \ref{tab:fn_req}. The functional requirements and their acceptance criteria are also listed in the same table, with prioritization based on the severity of consequences for the system. The first six functional requirements prioritize safety and robustness, while functional requirements seven to nine focus on increasing robot autonomy with lower risk potential.

@@

This work focuses on extending the capabilities of a mobile robot system by adding an autonomous layer to the existing navigation setup. The requirements for improving the robot's behavior were derived from the limitations of the current setup and are prioritized based on their severity. The autonomy layer is designed to increase the robustness and autonomy of the whole system and includes three main components: a system supervisor, a data storage system, and a behavior planner. The system supervisor monitors the health of all components, including sensors and navigation, and provides constant execution monitoring. The data storage system stores relevant system information and data, allowing for more deliberative behaviors. The behavior planner processes information from the execution checker, the navigation system, and sensor data to make decisions on how to increase autonomy. Finally, a decision gate is needed to intelligently switch between velocity commands from the navigation system and the autonomy layer. A block diagram of the proposed system is shown in Figure \ref{fig:block_diagram}.

@@

The system supervisor component uses a Watchdog design pattern to monitor the system and take corrective measures when problems are detected. The component operates partly outside the behavior tree's thread to avoid blocking its execution. The component receives messages from nodes and informs the behavior tree of problems with a node through a provided service. The behavior tree uses service calls to check component health in Condition Nodes. If a node fails, the robot slows down and tries to restart the node. If the restart fails twice, the robot stops. The timeout for declaring a node failed is set to one second.

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.5\linewidth]{Figures/top_level_bt.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure*}

@@

The battery behavior monitors the robot's battery and decides if the robot should navigate to a given goal. The decision is based on the current battery charge and the estimated energy consumption to reach the new goal. The energy expenditure was predicted using a linear function and considering the idle consumption and energy to drive the motors. A safety factor was added to the energy estimation function to consider scenarios where the robot may need to stop navigation.. A battery package was created for simulation purposes and updates the battery charge every second. The battery package subscribes to the command velocity topic and decreases the battery charge for every message received. The consumption rates are not close to reality but were chosen for rapid testing.

@@

The battery module estimates the remaining charge by taking the battery voltage, the power consumption of every component and the movement of the robot into account thus assuring that the robot has enough charge left to navigate to a given goal. Following function is used to determine the current state of charge of the battery: \[Batt_{SoC}(t) = Batt_{SoC}(t-1)-\frac{\frac{P_{components}}{V_{measured}}}{Batt_{capacity}}* t_{timestep} *100\] where $Batt_{SoC}$ is the charge in percentage, $t$ the time of calculation in hours, $V_{measured}$ the voltage measurements of the ROSBot, $Batt_{capacity}$ the capacity of the battery pack, $t_{timestep}$ the time step in seconds and $P_{components}$ the combined power consumption of every component connected to the robot in Watt. $P_{components}$ changes depending on the speed of the robot. The calculation assumes a fully charged battery.

@@

The scenarios, derived from functional requirements, test multiple requirements as listed in tables \ref{tab:behavior_scenarios} and \ref{tab:sensor_scenarios}. To be counted as a success, all acceptance criteria for a scenario must be met. The scenarios are conducted by shutting down sensor drivers, publishing navigation goals, and simulating obstacles and battery conditions. Examples include: NoPathFound$\_1$ tests recovery from inability to plan, NoPathFound$\_2$ tests alternative goal navigation, Collision$\_1$ tests maneuvering out of collisions, Collision$\_2$ tests recovering from crashes, and Battery$\_1$ tests low battery navigation.

\begin{table}[ht]
	\centering
	\caption{Behavior Scenarios}
	\label{tab:behavior_scenarios}
	\renewcommand{\arraystretch}{1.25}
	\resizebox{0.99\linewidth}{!}{%
		\begin{tabular}{| m{0.15\linewidth} | m{0.19\linewidth}| m{0.3\linewidth} | m{0.4\linewidth}|} 
			\hline
			\textbf{Name} & \textbf{Requirements} & \textbf{Description} & \textbf{Success Criteria}\\ 
			\hline	
			NoPath Found$\_$1 & fn$\_$req7 & Path to goal can not be calculated, robot is standing still & 
			Reset system, calculate path to goal, reach goal \\
			\hline
			NoPath Found$\_$2 & fn$\_$req7, fn$\_$req8 & Goal is unreachable, robot is standing still & Alternative goals, close to the original are tested to be reachable \\
			\hline
			Collision$\_$1 & fn$\_$req2, fn$\_$req4, fn$\_$req6 & Robot is standing still and a collision with the robot is caused & Robot can get out of collision state, navigation to goals still working \\
			\hline
			Collision$\_$2 & fn$\_$req2, fn$\_$req4, fn$\_$req6 & The robot is driving and collides with an undetected obstacle (0.25m/s) & 
			Robot can get out of collision state, navigation to goals still working, undetected obstacle gets added to map \\
			\hline
			Battery$\_$1 & fn$\_$req9 & The robot battery runs low & The robot will not drive to a goal that is outside of its reachable range \\
			\hline	
		\end{tabular}
	}
\end{table}

\begin{table}[ht]
	\centering
	\caption{Sensor Scenarios}
	\label{tab:sensor_scenarios}
	\renewcommand{\arraystretch}{1.25}
	\resizebox{0.99\linewidth}{!}{%
		\begin{tabular}{| m{0.12\linewidth}| m{0.1\linewidth} | m{0.22\linewidth}| m{0.5\linewidth} | m{0.08\textwidth}|} 
			\hline
			\textbf{Sensor Tested} & \textbf{Name} & \textbf{Requirements }& \textbf{Description} & \textbf{Success Criteria}\\ 
			\hline
			& Lidar$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, Lidar node crashes & Reset system\\ 
			\cline{2-5}
			Lidar &Lidar$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			& Lidar$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
			& IMU$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, IMU node crashes & Reset system \\
			\cline{2-5}
			IMU &IMU$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			&IMU$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
			& Odom$\_$1 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Robot is standing still, Odom node crashes & Reset system\\ 
			\cline{2-5}
			Odometry &Odom$\_$2 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s straight towards goal (1m away) & Reset system, reach goal \\ 
			\cline{2-5}
			&Odom$\_$3 & fn$\_$req1, fn$\_$req2, fn$\_$req3, fn$\_$req4, fn$\_$req5 & Navigating with 0.25 m/s and 0.5 rad/s towards goal (1m away) & Reset system, reach goal\\
			\hline
		\end{tabular}
	}
\end{table}

@@

\begin{table}[ht]
	\centering
	\caption{Results}
	\label{tab:results}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.99\linewidth}{!}{%
		\begin{tabular}{| m{0.25\linewidth} | m{0.15\linewidth}| m{0.15\linewidth} | m{0.15\linewidth}| m{0.15\linewidth}| m{0.15\linewidth}|} 
			\hline
			\multirow{2}{*}{\textbf{Name}} & \multirow{2}{0.11\textwidth}{\textbf{Number of Runs}} & \multicolumn{4}{|c|}{\textbf{Percentage Successful}} \\
			\cline{3-6}
			& & \multicolumn{2}{|c|}{Without BT} & \multicolumn{2}{|c|}{With BT} \\
			\cline{3-6}
			& & \textbf{Simulation} & \textbf{Real World} & \textbf{Simulation} & \textbf{Real World} \\		
			\hline
			Lidar$\_$1 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			Lidar$\_$2 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			Lidar$\_$3 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			IMU$\_$1 & 5 & 0 &  0& 100 &100\\ 
			\hline
			IMU$\_$2 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			IMU$\_$3 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			Odom$\_$1 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			Odom$\_$2 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			Odom$\_$3 & 5 & 0 & 0 & 100 &100\\ 
			\hline
			NoPath Found$\_$1 & 20 & 0 & 0 & 100 &100\\ 
			\hline
			NoPath Found$\_$2 & 20 & 0 & 0 & 55 &30\\ 
			\hline
			Collision$\_$1 & 20 & 0 & 0 & 95 &60\\ 
			\hline
			Collision$\_$2 & 20 & 0 & 0 & 100 &75\\ 
			\hline
			Battery$\_$1 & 10 & 0 & 0 & 100 &100\\ 
			\hline
		\end{tabular}
	}
\end{table}

However, there is a lack of intelligence and autonomy when the robot stands still, and a collision is forced. The test showed potential shortcomings of the implemented collision behavior. The results show that the functional requirements (as defined in \ref{tab:fn_req}) are met in almost all cases, with the exception of fn$\_$req6 and fn$\_$req8. The architectural design choices meet all the non-functional requirements. The system's performance when checking the conditions of the BT is below the desired threshold of $10ms$, allowing for efficient execution of behavior tree cycles.

The system also performed well in terms of performance, with the whole system running in multiple threads, allowing the behavior tree to complete one complete execution cycle in about $5ms$. Overall, the results suggest that the implemented behavior planning and system supervision system is a promising solution for autonomous navigation in complex environments.
